---
title: "Lab 01 - Hello R!"
date: "2018-01-18 (updated `r Sys.Date()` by TL)"
author: "Mine Cetinkaya-Rundel and colleagues"
output: 
  html_document: 
    self_contained: no
  tufte::tufte_html:
    tufte_variant: "envisioned"
    highlight: pygments
    css: lab.css
    link-citations: yes
    self_contained: FALSE
---

```{r include=FALSE}
library(tidyverse)
library(datasauRus)
options(
  htmltools.dir.version = FALSE, # for blogdown
  show.signif.stars = FALSE     # for regression output
  )
```



```{r}
library(tidyverse)
library(datasauRus)
?datasaurus_dozen
colnames(datasaurus_dozen)
```
There are 1846 rows and 3 columns from the help file
The variable names are "dataset", "x", and "y"


```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```



```{r fig.fullwidth=TRUE}
dino_data = datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r}
dino_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient is -0.06447185.

```{r}
star_data = datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
```{r}
star_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient between x and y is -0.0629611.
The correlation coefficient is also very small, compared with that of the dino_data. It tells that there is weak linear relationship between x and y.

```{r}
circle_data = datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
```{r}
circle_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient between x and y is -0.06834336.
The correlation coefficient is also very small, compared with that of the dino_data and star_data. It tells that there is weak linear relationship between x and y.


